---
title: "P8105_HW1_kw3103"
author: "Kairui Wang"
date: "2023-09-21"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)

library(moderndive)
```

# Problem 1

* Load the dataset.

```{r}
data("early_january_weather")
```

A short description about the dataset:
The dataset has `r nrow(early_january_weather)` observations of `r ncol(early_january_weather)` variables. And the variables included in this data set are `r colnames(early_january_weather)`. The mean temperature recorded in early January 2013 was `r round(mean(early_january_weather$temp),2)` degrees.

* Make a scatterplot.

```{r}
ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()
```

A description of this plot: 
As shown in the graph, the temperature spirals upward over time and the humidity increases with temperature

* Save the plot.

```{r, message = FALSE}
ggsave('early_january_weather.png')
```


# Problem 2

* Create a data frame

```{r}
df <- tibble(
  samp = rnorm(10),
  vec_logical = samp>0,
  vec_char = c('q','w','e','r','t','y','u','i','o','p'),
  vec_factor = c('1','2','1','2','1','2','3','3','2','3')
  )

print(df)
```

* Take the mean of each variable
** Use 'pull' function to pull the variable out of the dataframe.

```{r}
mean(pull(df,samp))

mean(pull(df,vec_logical))

mean(pull(df,vec_char))

mean(pull(df,vec_factor))
```

As we can see, the **samp** & **vec_logical** works and **vec_char** & **vec_factor** doesn’t.

* Applies the as.numeric function to the logical, character, and factor variables

```{r, convert, eval = FALSE}
as.numeric(pull(df,vec_logical)
           
as.numeric(pull(df,vec_char))

as.numeric(pull(df,vec_factor))
```

```{r, results = FALSE, warning = FALSE}
mean(as.numeric(pull(df,vec_logical)))

mean(as.numeric(pull(df,vec_char)))

mean(as.numeric(pull(df,vec_factor)))
```

The mean of the logical vector is 0.5.

The mean of the character vector is NA.

The mean of the factor vector is 2.

This is because factor variables can be converted to numeric variables because the factors have corresponding levels, which are what R uses when converting variables to numeric variables.